Peace Science Society

### 2023-06-03 presentations/2022-11-04_peace-science/index.qmd
Better handling of slide resources

---
title: "Peace Science Society"
date: 2022-11-04
toc: false
resources: slides
abstract: |
  Annual conference of the Peace Science Society; Denver, Colorado
abstract-title: "Location"
published-title: "Presented"
image: first-slide.png
page-layout: full
---

>>>>

---
title: "Peace Science Society"
date: 2022-11-04
toc: false
abstract: |
  Annual conference of the Peace Science Society; Denver, Colorado
abstract-title: "Location"
published-title: "Presented"
image: first-slide.png
page-layout: full
---
